\documentclass[english,a4paper]{article}
\usepackage[]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[letterpaper, margin=1in, tmargin=20pt]{geometry}
\usepackage{babel}
\usepackage{titlesec}
\usepackage{enumitem}

\setlist{noitemsep}

\titleformat{\section}{\Large}{Article \Roman{section}.}{10pt}{}
\titlespacing{\section}{0pt}{0.5em}{0.5em}

\renewcommand{\labelenumi}{\S\arabic{enumi}}

\title{Constitution \textit{of the} eXperimental Computing Facility\vspace{-3ex}}
\date{Ratified September 2019\vspace{-3ex}}

\begin{document}

\maketitle

\section{Name}
\begin{enumerate}
\item The name of this organization is eXperimental Computing Facility,
  abbreviated XCF.
\end{enumerate}
\section{Purpose}

\begin{enumerate}
\item The XCF is an engineering collaboration dedicated to building visionary,
  useful software for the University and the community at large.
\end{enumerate}


\section{Activities}


\begin{enumerate}
\item As part of its mission, the XCF will design, build, enhance, and
  maintain applications that provide ongoing benefit to the University
  and the general computing community.
\end{enumerate}

\section{Membership}

\begin{enumerate}
\item Any UC Berkeley student, faculty, or staff member may be an XCF member.
  Only active members may vote or hold office.

\item We will not haze according to California State Law. We will not restrict
  membership based upon race, color, national origin, religion, sex,
  gender identity, pregnancy (including pregnancy, childbirth, and medical
  conditions related to pregnancy or childbirth), physical or mental
  disability, medical condition (cancer related or genetic characteristics),
  ancestry, marital status, age, sexual orientation, citizenship, or
  service in the uniformed services (including membership, application
  for membership, performance of service, application for service, or
  obligation for service in the uniformed services).
\end{enumerate}

\section{Officers}

\begin{enumerate}

\item The XCF shall convene to nominate and elect new officers at the beginning of every semester. All non-signatory officers
  are subject to re-election every semester.

\item Officers shall be elected by majority vote of members pursuant to Art. VI $\S$ 2.

\item A majority vote of officers shall designate posts, committees, and
  honorary members, and may modify the membership requirements in Article IV provided other administrative requirements are met.

\end{enumerate}

\section{Meetings}

\begin{enumerate}
\item
  Officers shall convene XCF meetings at least four times per semester.

\item
  XCF officer nominations and elections shall occur within the first
  two meetings of the semester.

\end{enumerate}
\section{Constitutional Amendments}

\begin{enumerate}
\item
  A majority of officers may propose amendments to this document, which must be ratified by a supermajority of all active members.

\item
  All amendments, additions, or deletions to this document shall be
  filed with the LEAD Center in 432 Eshleman Hall.
\end{enumerate}
\section{Dissolution}
\begin{enumerate}

\item
  A supermajority of active members and officers may vote to dissolve
  this organization.

\item
  If the organization is ASUC or GA Sponsored, all unspent ASUC funds
  shall return to the ASUC; all Graduate Assembly funds shall return
  to the Graduate Assembly. If the organization is defunct for five
  (5) or more years, any privately obtained funds (including any funds
  left in miscellaneous accounts) shall be donated to the ASUC Open Computing
  Facility.
\end{enumerate}

\end{document}
